High-Dim Project

### 2014-12-18 highdim-paper/paper.tex
Fixed the previous merge issue

<<<<<<< HEAD
%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

@@

$minimize_{W \in R^{d x m}} F(W) = $

$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } max(1 - W_{:y_i} \cdot x_i + W_{:r} \cdot x_i , 0 )^2 $

$ + \lambda \sum_{g=1}^{|G|} \sum_{m=1}^{d} \| W_{g,m} \|_2$ \\

The first term is the multiclass squared hinge loss function. We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible. And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it. In the second term, $W_{g,m}$ means a block of weights in group $g$ and class $m$. The L2 norm regulization is computed and sum up for each block. The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.  \\

\subsection{Artificial data}

\begin{figure}[ht]
\begin{center}
	\includegraphics[natwidth=200, natheight=306]{m_img}
	\caption{Group-wise sparse weight matrix generated: 6 classes, 30 features in 5 groups}
\end{center}
\end{figure}

Then we generate random vectors, each of which has the length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors. The random vetors X and the class assignments Y make up the training data set. \\

\end{document}
=======
%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

\author{name1 \\
  Columbia University\\
  {\small \tt uni1@columbia.edu} \\\And
  name2 \\
  Columbia University\\
  {\small \tt uni2@columbia.edu} \\\And
  name3\\
  Columbia University\\
  {\small \tt uni3@columbia.edu} \\}
\date{}

\section{Introduction}

@@

\end{document}
>>>>>>> FETCH_HEAD

>>>>

%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

@@

@@

\end{document}
